\begin{frame}{Stages of IPS}
	\begin{itemize}
		\item Involves 4 stages of operations.
		\item Initialization of price, volatility.
		\item $n$ loops of:
		      \begin{itemize}
		      	\item Selection stage to select paths that could lead to the
		      	      rare event of higher defaults.
		      	\item Mutation stage to evolve the selected paths as per the
		      	      SDEs.
		      \end{itemize}
		\item Termination stage to collect result of previous stage and estimate
		      default probabilities.
	\end{itemize}
\end{frame}

\begin{frame}{Initialization}
	\begin{block}{Initial Value}
		\begin{equation*}
			\begin{split}
				\hat{X}_0^{(j)} &= \left( \sigma(0), S_1(0), \cdots, S_N(0), S_1(0), \cdots, S_n(0) \right),  \quad 
				\forall 1 \leq j\leq M                                                                    \\
				\hat{W}_0^{(j)} &= \hat{X}_0^{(j)}
			\end{split}
		\end{equation*}
	\end{block}
	\begin{itemize}
		\item All $M$ portfolios are started with the same price and volatility.
		\item Initial minimum is same as initial price.
		\item Initial history is same as current initialization.
	\end{itemize}
\end{frame}

\begin{frame}{Selection}
	\begin{itemize}
		\item Resample with replacement $M$ paths from input $M$ paths according
		      to empirical distribution under the given Gibbs measure.
		\item $\left( \hat{W}_p^{(j)}, \hat{X}_p^{(j)} \right)$ becomes $\left( \breve{W}_p^{(j)}, \breve{X}_p^{(j)}\right)$.
	\end{itemize}
	\begin{block}{Empirical distribution}
		\begin{equation*}
			\begin{split}
				&\eta_{p}^{M}(dW,dX) = \frac{1}{M \hat{\eta}_{p}^{M}}\sum_{j=1}^{M}\exp\left[{\alpha(V(\hat{X}_{p}^{(j)}))-V(\hat{W}^{(j)}_{p})}\right] \times \delta_{(\hat{W}_p^{j},\hat{X}_p^{j})}(dW,dX) \\
				&\text{Where}\\
				&\hat{\eta}_{p}^{M} =
				\frac{1}{M}\sum_{j=1}^{M}\exp\left[{\alpha(V(\hat{X}_{p}^{(j)}))-V(\hat{W}^{(j)}_{p})}\right]
			\end{split}
		\end{equation*}
	\end{block}
\end{frame}

\begin{frame}{Mutation}
	\begin{itemize}
		\item Evolve paths from $\breve{X}_p^{(j)}$ to $\hat{X}_{p+1}^{(j)}$.
		\item Set $\hat{W}_{p+1}^{(j)} = \breve{X}_p^{(j)}$.
		\item Evolve based on SDEs using Euler-Maruyama method with time step
		      $\delta t$. Evolution is from $t_p$ to $t_{p+1}$ ($t_p + \Delta t$).
		\item $\delta t \ll \Delta t$
		\item True Dynamics.
	\end{itemize}
\end{frame}

\begin{frame}{Termination}
	\begin{itemize}
		\item Teminate at maturity time $T$ by running the selection, mutation
		      step $n$ times. ($n \Delta t = T$)
		\item Estimate default probability $p_k(T) = \mathbb{P}\left( L\left( T \right) = k
		      \right)$ using formula below.
	\end{itemize}
	\begin{block}{Estimation}
		\begin{equation*}
			\begin{split}
				&\hat{p}_{k}^{M}(T) = \left[ \frac{1}{M} \sum_{j=1}^{M} \mathbf{1}_{\lbrace f(\hat{X}_{n}^{(j)}) = k\rbrace
						}\exp\left[{\alpha(V(\hat{W}^{(j)}) - V(\hat{X_{0}}))}\right]\right] \times \left[ \prod_{p=0}^{n-1} \hat{\eta}_{p}^{M}\right] \\
						&\text{Where}\\
						&f(X^{(j)}_n) = \sum_{i=1}^{N}\mathbf{1}_{\lbrace X^{(j)}_{n}(N + 1 + i)\leq B_{i}\rbrace}
					\end{split}
				\end{equation*}
			\end{block}
		\end{frame}
